Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-12-11 paper/main.tex
change order of authors
add reminders
fixup! rename folder

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/snapshots/predicted-003889.png}%
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/celldiffs/diff-003889.png}%
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        (A) Final microscopic image of the time series with the predicted positions of the cells
        overlayed on top.
        (B) Differences between extracted and predicted positions.
        Note that the image-space metric was not used to optimize this system but is
        chosen here as a tool to aid visualization of the prediction difference.
    }
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/damping.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/exponent-m.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/exponent-n.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/strength.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/radius.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{H}};
    \end{tikzonimage}%
    \caption{
        (A-H) Likelihood profiles of optimized parameters.
        Bands of blue and yellow represent confidence intervals of $68\%,90\%$ and $95\%$.
        \textbf{TODO adapt this description to new results}
        Every plot indicates that a minimum was achieved, thus every parameter could be identified.
        We show only one of the 6 individually-chosen growth rate as an example.
        The remaining plots show similar behavior although with varying values and can be found in
        the supplementary material (Section~\ref{sec:supplement-parameter-profiles}).
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000000.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000001.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000002.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000003.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000004.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000006.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000007.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{H}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000008.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{I}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000009.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{J}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000010.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{K}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000011.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{L}};
    \end{tikzonimage}%
    \caption{
        \text{TODO include missing profiles here}
        Likelihood profiles of every estimated parameter.
        (A-D) Division Lengths of initially placed cells.
        (E-H) Growth rates of daughter cells.
        The growth rates diplay larger values of noise within their profiles compared to the
        division lengths.
        \textbf{TODO possibly extend this description?}
    }
    \label{fig:likelihood-profiles-comparison-with-division}
\end{figure}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{l c c c c c c}
        \multicolumn{4}{l}{\textbf{Growth Parameters for different Methods}}\\
        \toprule
        % \multicolumn{6}{Growth Rates}\\
        Method & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \midrule
        Fit             & 0.00703 & 0.00540 & 0.01159 & 0.00756 & 0.01024 & 0.00836\\
        \ac{abm} Direct & 0.00671 & 0.00746 & 0.01138 & 0.00848 & 0.02005 & 0.00952\\
        \ac{abm} Imaging& 0.00104 & 0.00146 & 0.00206 & 0.00286 & 0.00190 & 0.00171\\
        & \textbf{Daughters}\\
        \midrule
        & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        & 0.00240 & 0.00494 & 0.00096 & 0.00363\\
        & 0.00490 & 0.00226 & 0.00448 & 0.00048\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{TODO maybe report uncertainties?;
        Update and explain these values. And also add units!;
        FIX NUMERICAL VALUES;
        check ordering of values}
    }
    \label{tab:comparison-growth-rates}
\end{table}

@@

%TODO {explain profiles}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/profiles/growth-rate-5.pdf}
    \caption{Parameter estimation of growth rates for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-growth-rates}
\end{figure}

@@

%###################################################################################################
\section*{Acknowledgements}
\paragraph{Author Contributions}
\textbf{Conceptualization:} Jonas Pleyer\\
\textbf{Investigation:} Jonas Pleyer\\
\textbf{Methodology} Jonas Pleyer\\
\textbf{Software:} Jonas Pleyer\\
\textbf{Supervision:} Christian Fleck\\
\textbf{Writing – original draft:} Jonas Pleyer\\
\textbf{Writing – review \& editing:} Christian Fleck \& Jonas Pleyer

>>>>

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/mie/snapshots/predicted-003889.png}%
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{A}};
    \end{tikzonimage}%
    \hspace{0.01\textwidth}%
    \begin{tikzonimage}[width=0.49\textwidth]
        {figures/crm_fit/mie/celldiffs/diff-003889.png}%
        \node at (0.025, 0.975)[anchor=north west, white]{\textbf{B}};
    \end{tikzonimage}%
    \caption{
        (A) Final microscopic image of the time series with the predicted positions of the cells
        overlayed on top.
        (B) Differences between extracted and predicted positions.
        Note that the image-space metric was not used to optimize this system but is
        chosen here as a tool to aid visualization of the prediction difference.
    }
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/damping.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/exponent-m.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/exponent-n.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/strength.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/radius.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-0.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-1.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-2.pdf}%
        \node at (0, 1.1)[anchor=north west, black]{\textbf{H}};
    \end{tikzonimage}%
    \caption{
        (A-H) Likelihood profiles of optimized parameters.
        Bands of blue and yellow represent confidence intervals of $68\%,90\%$ and $95\%$.
        \textbf{TODO adapt this description to new results}
        Every plot indicates that a minimum was achieved, thus every parameter could be identified.
        We show only one of the 6 individually-chosen growth rate as an example.
        The remaining plots show similar behavior although with varying values and can be found in
        the supplementary material (Section~\ref{sec:supplement-parameter-profiles}).
    }
    \label{fig:parameter-estimates-single-step}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000000.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000001.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000002.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000003.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000004.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000006.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000007.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{H}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000008.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{I}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000009.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{J}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000010.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{K}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000011.png}%
        \node at (0.15, 0.85)[anchor=north west, black]{\textbf{L}};
    \end{tikzonimage}%
    \caption{
        \text{TODO include missing profiles here}
        Likelihood profiles of every estimated parameter.
        (A-D) Division Lengths of initially placed cells.
        (E-H) Growth rates of daughter cells.
        The growth rates diplay larger values of noise within their profiles compared to the
        division lengths.
        \textbf{TODO add profiles for daughter cells}
        \textbf{TODO possibly extend this description?}
    }
    \label{fig:likelihood-profiles-comparison-with-division}
\end{figure}

@@

\begin{table}[H]
    \centering
    \begin{tabular}{l c c c c c c}
        \multicolumn{4}{l}{\textbf{Growth Parameters for different Methods}}\\
        \toprule
        % \multicolumn{6}{Growth Rates}\\
        Method & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        \midrule
        Fit             & 0.00703 & 0.00540 & 0.01159 & 0.00756 & 0.01024 & 0.00836\\
        \ac{abm} Direct & 0.00671 & 0.00746 & 0.01138 & 0.00848 & 0.02005 & 0.00952\\
        \textbf{Imaging values will be adjusted!}\\
        \ac{abm} Imaging& 0.00104 & 0.00146 & 0.00206 & 0.00286 & 0.00190 & 0.00171\\
        & \textbf{Daughters}\\
        \midrule
        & Cell $0$ & Cell $1$ & Cell $2$ & Cell $3$ & Cell $4$ & Cell $5$\\
        & 0.00240 & 0.00494 & 0.00096 & 0.00363\\
        & 0.00490 & 0.00226 & 0.00448 & 0.00048\\
        % 0.0014057073 & 0.0010807540 & 0.0023177727 & 0.0015120675 & 0.0020488179 & 0.0016726263\\
        % direct & 0.0009785162 & 0.0012641432 & 0.0021701728 & 0.0015695889 & 0.0036255661 & 0.0018419186\\
        \bottomrule
    \end{tabular}
    \caption{
        \textbf{TODO maybe report uncertainties?;
        Update and explain these values. And also add units!;
        FIX NUMERICAL VALUES;
        check ordering of values}
    }
    \label{tab:comparison-growth-rates}
\end{table}

@@

%TODO {explain profiles}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-0.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-1.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-2.pdf}\\%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-3.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-4.pdf}%
    \includegraphics[width=0.33\textwidth]
        {figures/crm_fit/mie/profiles/growth-rate-5.pdf}
    \caption{Parameter estimation of growth rates for individual cells}%TODO extend caption}
    \label{fig:parameter-estimates-supplement-growth-rates}
\end{figure}

@@

%###################################################################################################
\section*{Acknowledgements}
\paragraph{Author Contributions}
\textbf{Conceptualization:} Jonas Pleyer\\
\textbf{Investigation:} Jonas Pleyer\\
\textbf{Methodology} Jonas Pleyer\\
\textbf{Software:} Jonas Pleyer\\
\textbf{Supervision:} Christian Fleck\\
\textbf{Writing – original draft:} Jonas Pleyer\\
\textbf{Writing – review \& editing:} Jonas Pleyer \& Christian Fleck
